Predator clusters

### 2023-06-07 reports/04_pred_clus.qmd
Include 2014 ice data
updated targets meta after fixing ice data

station_ice <- predators_stations %>% 
  group_by(amlr.station) %>%

  summarize(ice_type = ice_type[1]) %>% 
  as_tibble() %>% 
  select(-geometry)

@@

layout <- "
AAAA
BBCC
"
hydro_plot + ice_plot + zoop_plot + 
  plot_layout(design = layout, guides = "collect")
```

>>>>

station_ice <- predators_stations %>% 
  distinct(amlr.station, ice_type, ice_coverage) %>% 
  as_tibble()

@@

layout <- "
AAAA
AAAA
BBCC
"
hydro_plot + ice_plot + zoop_plot + 
  plot_layout(design = layout, guides = "collect")
```
